NIRCam Calibration Plan

### 2016-12-17 ms.tex
I added some isochrones to justify the age choices.

Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
The parameters under consideration were the the following:
\begin{itemize}
\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence. This means the age of the cluster must be between 0.2 Gyr (??) and 8 Gyr (??) using Dartmouth evolutionary models \citep{dotter2008dartmouth}.
\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. This generally means E(B-V) $\lesssim < 0.1$.
\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode.
\item {\bf Metallicity}
\item {\bf Compactness}
\item {\bf Ancillary data}
\end{itemize}

@@

Funding for the NIRCam team is provided by NASA Goddard Spaceflight Center. This research has made use of the WEBDA database, operated at the Department of Theoretical Physics and Astrophysics of the Masaryk University.
Observations reported here were obtained at the MMT Observatory, a joint facility of the University of Arizona and the Smithsonian Institution.
This paper uses data products produced by the OIR Telescope Data Center, supported by the Smithsonian Astrophysical Observatory.
The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, the Max-Planck Society and its participating institutes, the Max Planck Institute for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las Cumbres Observatory Global Telescope Network Incorporated, the National Central University of Taiwan, the Space Telescope Science Institute, the National Aeronautics and Space Administration under Grant No. NNX08AR22G issued through the Planetary Science Division of the NASA Science Mission Directorate, the National Science Foundation under Grant No. AST-1238877, the University of Maryland, and Eotvos Lorand University (ELTE) and the Los Alamos National Laboratory.

@@

Zodiacal background is expressed as a function of the minimum zodiacal background in \texttt{pynrc}.
From the code documentation: average across the sky has zfact = 2.5.

>>>>

Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
The parameters under consideration were the the following:
\begin{itemize}
\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence. If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}. Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. This generally means E(B-V) $\lesssim < 0.1$.
\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode.
\item {\bf Metallicity}
\item {\bf Compactness}
\item {\bf Ancillary data}
\end{itemize}

@@

Thanks to Daniel Kiminki and John Stauffer for the selection of open clusters for this work and for finding targets based on initial data.
Funding for the NIRCam team is provided by NASA Goddard Spaceflight Center. This research has made use of the WEBDA database, operated at the Department of Theoretical Physics and Astrophysics of the Masaryk University.
Observations reported here were obtained at the MMT Observatory, a joint facility of the University of Arizona and the Smithsonian Institution.
This paper uses data products produced by the OIR Telescope Data Center, supported by the Smithsonian Astrophysical Observatory.
The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, the Max-Planck Society and its participating institutes, the Max Planck Institute for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las Cumbres Observatory Global Telescope Network Incorporated, the National Central University of Taiwan, the Space Telescope Science Institute, the National Aeronautics and Space Administration under Grant No. NNX08AR22G issued through the Planetary Science Division of the NASA Science Mission Directorate, the National Science Foundation under Grant No. AST-1238877, the University of Maryland, and Eotvos Lorand University (ELTE) and the Los Alamos National Laboratory.

@@

Zodiacal background is expressed as a function of the minimum zodiacal background in \texttt{pynrc}.
From the code documentation: average across the sky has zfact = 2.5.
In these models solar B-V=0.65 for 1~M$_\odot$ at 4.25 Gyr.

\subsection{Isochrones}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.7\columnwidth]{hr_isochrones.pdf}
\caption{The Dartmouth isochrones \citep{dotter2008dartmouth}, for [Fe/H]=0, show that the age of the cluster should be $\lesssim 7 $Gyr before main sequence turnoff should begin to affect the identification of solar analogs.
The red vertical line represents solar B-V.}\label{fig:isochrones}
\end{figure}
